% LaTeX resume using res.cls
\documentclass[line]{resume}
\usepackage{scalefnt}
\usepackage{hyperref}
\hypersetup{colorlinks=false, pdfborder={0 0 0}}

\begin{document}

\name{Ryan V. McGowan}
\address{\href{https://www.ryanmcg.com}{Personal website --- https://www.ryanmcg.com}}
\address{\href{mailto:ryan@ryanmcg.com}{ryan@ryanmcg.com}}


\begin{resume}
    \vspace{-12pt}
    \section{\uppercase{Education}}

    \vspace{6pt}
    {\sl Bachelor of Science,} Computer Science \& Engineering \\
    The Ohio State University, Columbus, OH \\
    Graduated Magna Cum Laude in December 2012 \\

    \vspace{-10pt}

    \section{\uppercase{Overview}}
    \vspace{6pt}

    I am an engineer and leader who designs and builds software systems.
    I am well-versed in, and highly motivated by, risk-based problems (e.g. account security, fraud).
    \vspace{6pt}
    \begin{itemize}
        \item Leads engineers through large and complex projects by breaking
            down the problem with an attention to detail.
        \item Designs and builds fault-tolerant and scalable systems by crafting
            clean, maintainable code, and encouraging rigor in code and design
            with peers.
        \item Familiar with a variety of technologies (and excited to learn
            more): Python, Go, JavaScript, Ruby, Clojure, DynamoDB, Redis, HTTP,
            OAuth 2.0, Neptune (graph DB).
    \end{itemize}

    \vspace{6pt}

    \section{\uppercase{Experience}}
    \vspace{6pt}

    {\sl\textbf{Staff Engineer, Tech Lead}} \hfill January 2020--June 2023\\
    \emph{Identity at \underline{\href{https://www.lyft.com/}{Lyft}}}
    \begin{itemize}
        \item Continued ownership and execution of team's technical components and long-term
            vision including graph DB, identity proofing solutions
        \item Pitched, got buy-in and executed on building Lyft's first native-graph-DB-backed service. Advised a new team built around that service. Today it is used to power multi-hop features used in rules and models saving \$ millions yearly.
	\item Designed and led implementation of solution to severe driver safety incidents in major markets which exposed Lyft to millions in insurance and PR risk. MVP launched in a month with a cross-functional team.
	\item Led multi-team, cross-functional solution to driver acquisition abuse (costing \$10M+ annually). Broke the problem down, defined it and brought along leadership with clear docs. Addressed concerns by testing previous identity proofing solutions and addressing their gaps with the new fraud vector. Leveraged incremental technical solutions instead of building from scratch and taking more time and resources.
        \item Successfully mentored team members through career pathway and
            promotions.
    \end{itemize}
    \vspace{6pt}

    {\sl\textbf{Software Engineer, Tech Lead}} \hfill March 2016--January 2020\\
    \emph{Identity at \underline{\href{https://www.lyft.com/}{Lyft}}}
    \begin{itemize}
        \item Led a team of 10 engineers including crafting of long-term
            technical vision.
        \item Designed, built, and owned key services handling millions of
            requests per minute. Two of my services were taken on by other teams
            and have stood the test of time. 
        \item Designed and developed solutions to
	    Recycled phone numbers (existential problem), duplicate accounts, lyft.com authentication,
            account recovery.
        \item Supported team members solving a myriad of other problems: \\
            Third party identity linking, account take over, unauthorized
            driving.
        \item Key contributor to risk/fraud rule engine and challenges
            infrastructure.
    \end{itemize}
    \vspace{6pt}

    {\sl\textbf{Software Development Engineer}} \hfill July 2013--January
    2016\\
    \emph{Information Security, Review Automation at
    \underline{\href{http://www.amazon.com/}{Amazon}}}
    \begin{itemize}
        \item Improved the quality and stability of product by emphasizing code
            maintainability.
        \item Mentored several new hires and interns.
        \item Implemented a computed-observable based client-side application
            library on top of React.
    \end{itemize}
    \vspace{6pt}

    {\sl\textbf{Software Engineer}} \hfill Janurary 2013--June 2013\\
    \emph{\underline{\href{http://www.facio.com/}{Facio}}} ---
    Contributed to core backend and frontend components.
    \vspace{6pt}

\end{resume}

\end{document}
